The colors are chosen from the base R colors. 

```{r}
# creates S4 class called "palette"
setClass("palette", #name 
        representation(
            classification = "character", #list
            size = "numeric", #size is always 3
            cb_friendly = "logical", #color blind frinedly 
            colors = "vector" #palette colors returned here 
  )
)

```


df : 657 rows, 3 columns. 
    rows: correspond to the index of the built-in R colors 
    ex. df[47] corresponds to the 47th color of built-in R colors
    columns: correspond to the RBG value of the color

colors_df : 657 rows, 1 column
    rows: color name
    columns: "colors"
blue_colors : subset of the df where the color is clearly a shade of blue. 
              for all such colors the rbg blue value = 255 and red is less than 
              or equal to 128
red_colors : subset of the df where the color is clearly a shade of red. 
             for all such colors the rbg red value = 255 and blue is less than 
             or equal to 128
green_colors : subset of the df where the color is clearly a shade of green. 
               for all such colors the rbg green value = 255 and red is less than 
               or equal to 128

```{r}
#creates a df of optimal colors. see above for more details.
colorframe <- function(){
    df <- data.frame(col2rgb(colors(), alpha = FALSE)) #color df with Hex
    df <- as.data.frame(t(df)) #transpose 
    colors_df <- (data.frame(colors())) #creates color df with names
    blue_colors <- df[df$blue == 255 & df$red <= 128, ] #blue colors
    green_colors <- df[df$green == 255 & df$red <= 128, ]#green colors
    red_colors <- df[df$red == 255 & df$blue <= 128, ] #red colors
    
    return(list(
            colors_df = colors_df,
            blue_colors = blue_colors,
            green_colors = green_colors,
            red_colors = red_colors
))
}

```

When an individual is red/green color blind, it means they experience distinguish red or green from one
another because of defective receptors in the eyes. A color palette containing either green or red aims to 
eliminate some of the difficulties a colorblind person experiences.

```{r}
# creates the color palette
palette <- function(colors){
    green_colors <- colors$green_colors
    blue_colors <- colors$blue_colors
    red_colors <- colors$red_colors

    # first color: red OR green
    color1 <- sample(c(
    sample(rownames(green_colors), 1),
    sample(rownames(red_colors), 1)
    ), 1)
   
    # second color: blue
    color2 <- sample(rownames(blue_colors), 1)

    # third color: a color that is not explicitly a shade of red/green/blue
    original_colors <- df[!(rownames(df) %in% c(
    rownames(blue_colors),
    rownames(red_colors),
    rownames(green_colors)
    )), ]

    color3 <- rownames(original_colors)[sample(nrow(original_colors), 1)]

    #create color palette
    selected_colors <- gsub("X", "", c(color1, color2, color3))
    interior_palette <- as.vector(as.matrix(colors_df[selected_colors, , drop = FALSE]))

    pal <- new("palette", classification = "color palette", size = 3, cb_friendly = TRUE, colors = interior_palette)
    return(pal)
}

```


Let's run our functions!
```{r}
colordata <- colorframe()
cbpal <- palette(colordata)
cbpal@colors
```
